Contracts for Contracts

### 2023-06-15 paper/contract_solidity.tex
example of address guards using array of mapping

\paragraph{Multiple Targets}
Multiple callee targets can inhabit in a single address value.
Other than the \code{call} method, there are other forms of low-level call,
e.g., \code{delegatecall}, \code{send}, etc.
% https://docs.soliditylang.org/en/v0.8.20/units-and-global-variables.html#address-related
Programmers can specify conditions for different callee targets in the
\code{where}-clause.
\begin{lstlisting}
# f(addr) where
# { addr.send(x) returns (succ) requires ... }
# { addr.call(msg, x) returns (succ, data) requires ... }
\end{lstlisting}

@@

@@

\paragraph{Notes on Higher-Order Functions}
Functions in Solidity are first-class too, meaning that functions can be used
as arguments for and returned from functions. However, at this moment
\footnote{Solidity version 8.20} Solidity has not supported writing anonymous
functions (lambda expressions) or nested, named functions.
Only explicitly defined top-level functions can be used in first-class ways,
which effectively do not have capturing from the environment.
This restriction discourages programmers to use higher-order functions due to
its inconvenience and verbosity.
Moreover, it poses challenges to seamlessly implement first-class behavioral
contract and monitor system (e.g. as in \cite{DBLP:conf/icfp/FindlerF02})
without an expensive whole program transformation.
Therefore, in this paper we focus on the contract and monitoring of addresses
values and leave monitoring for higher-order functions as future work when
Solidity has a proper support for lambda expressions.

>>>>

\paragraph{Single Address, Multiple Callees}
Multiple callees can inhabit in a single address value.
Other than the \code{call} method, there are other forms of low-level calls with
different signatures, e.g., \code{delegatecall}, \code{send}, etc.
% https://docs.soliditylang.org/en/v0.8.20/units-and-global-variables.html#address-related
Programmers can specify conditions for different callee targets in the
\code{where}-clause.
\begin{lstlisting}
# f(addr) where
# { addr.send(x) returns (succ) requires ... }
# { addr.call(msg, x) returns (succ, data) requires ... }
\end{lstlisting}

@@

\paragraph{Second-Class Enforcement}
Addresses, as first-class values, can of course escape from a function, e.g.
by returning from the function or storing in external data structures.

Similarly, when a guarded address is used as an argument to another address
call, we lose the control of ...

@@

\paragraph{Notes on Higher-Order Functions}
Functions in Solidity are first-class too, meaning that functions can be used
as arguments for and returned from functions.
However, real closures following lexical scopes do not exist in Solidity
at this moment \footnote{Solidity version 8.20}.
There is no way to write anonymous functions (lambda expressions) or nested,
named functions that capture variables from environments.
Only explicitly defined top-level functions can be used in first-class ways.
This restriction discourages programmers to use higher-order functions due to
its inconvenience and verbosity.
Moreover, it poses challenges to seamlessly implement first-class behavioral
contract and monitor system that guards higher-order functions (e.g. as in
\cite{DBLP:conf/icfp/FindlerF02}) without an expensive whole program
transformation.
Therefore, in this paper we focus on the contract and monitoring of addresses
values and leave monitoring for higher-order functions as future work when
Solidity has a proper support for lambda expressions.
